ASHA 2023 Listening Effort Data Analysis

### 2023-10-31 ASHA 2023 Analysis/data_analysis.Rmd
Rendered rmd file
Started alternate figure
Code not working as intended yet. WIP

---
title: "ASHA 2023 Listening Effort Data Analysis"
author: "Micah E. Hirsch"
date: "2023-10-29"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

@@

control <- data %>%
  dplyr::filter(rep_acc == "accurate") %>%
  dplyr::filter(speaker == "Control") %>%
  ggplot() +
  aes(x = timebins,
      y = pupil.binned,
      color = speaker) +
  geom_smooth() +
  geom_vline(xintercept = 0, size = 0.35) +
  geom_vline(xintercept = 1908, linetype = 2) +
  annotate("rect", xmin = 500, xmax = 2908, ymin = -50, ymax = 150, alpha = 0.2) +
  coord_cartesian(xlim = c(0,4910), ylim = c(-100, 200)) +
  labs(title = "Control Speaker", x = "Time (ms)", y = "Pupil Dilation (arbitrary units)") +
  theme_bw() +
  scale_color_manual(values = my_pal[1]) +
  theme(legend.position = "none", aspect.ratio = 1)

@@

>>>>

---
title: "ASHA 2023 Listening Effort Data Analysis"
author: "Micah E. Hirsch"
date: "2023-10-30"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

@@

control <- data %>%
  dplyr::filter(rep_acc == "accurate") %>%
  dplyr::filter(speaker == "Control") %>%
  ggplot() +
  aes(x = timebins,
      y = pupil.binned,
      color = speaker) +
  geom_smooth() +
  geom_vline(xintercept = 0, size = 0.35) +
  geom_vline(xintercept = 1908, linetype = 2) +
  annotate("rect", xmin = 500, xmax = 2908, ymin = -50, ymax = 150, alpha = 0.2) +
  coord_cartesian(xlim = c(0,4908), ylim = c(-100, 200)) +
  labs(title = "Control Speaker", x = "Time (ms)", y = "Pupil Dilation (arbitrary units)") +
  theme_bw() +
  scale_color_manual(values = my_pal[1]) +
  theme(legend.position = "none", aspect.ratio = 1)

@@

```{r, include = F, eval = F}

bin.length = 26

data1 <- data %>%
  filter(speaker == "ALS") %>%
  group_by(code) %>%
  mutate(bins = round(timebins/bin.length)*bin.length) %>%
  group_by(subject, trial, bins, speaker, code) %>%
  dplyr::summarize(pupil = mean(pupil.binned)) %>%
  ungroup()

control <- data %>%
  filter(speaker == "Control") %>% 
  select(subject, trial, timebins, speaker, code, pupil.binned) %>%
  rename(pupil = pupil.binned,
         bins = timebins)

normed_pupil <- rbind(data1, control)

normed_pupil %>%
  count(speaker, code) %>%
  group_by(speaker) %>%
  summarize(row_m = mean(n), sd = sd(n))

normed_pupil %>%
  # Selecting relevant parameters
  dplyr::select(subject, trial, speaker, bins, code) %>%
  # Filtering out time before start of phrase
  dplyr::filter(bins >= 0) %>%
  dplyr::group_by(speaker, code) %>%
  dplyr::summarize(length = max(bins)) %>%
  dplyr::group_by(speaker) %>%
  dplyr::summarize(av_length = mean(length),
                   av_offset = av_length - 3000,
                   av_end_roi = av_length - 2000) %>%
  gt::gt() %>%
  gt::cols_label(speaker = "Speaker",
                 av_length = "Average Trial Length (ms)",
                 av_offset = "Average Phrase Length (ms)",
                 av_end_roi = "Average Endpoint for ROI (ms)")
